\bf Probabilistic Forecasts in Hierarchical~Time~Series

### 2020-01-22 R1/Response.tex

	\section*{Detailed Response to Referee 1: Major comments}

	\begin{enumerate}

		\item \textit{Lack of empirical contribution: The authors apply a couple of different transformations to the tourism data before constructing base forecasts. Failing to correctly transform the base forecasts back before they are reconciled introduces a bias. That the highest accuracy is obtained when applying the correct back-transformation is a very small contribution.}\\

		We agree that if our empirical results only showed that applying the correct back-transformation improves accuracy, that this would be a very marginal contribution.  The referee's suggestions have allowed us to make additional insights that we believe have greatly improved the paper.  We discuss these in detail below.\\

@@

		The observation regarding the constraints not holding on the log scale is correct.  When series are transformed to the log scale, forecasts are first produced on the log scale and these are back transformed to the original scale (possibly with bias correction) prior to carrying out reconciliation.  Therefore while all modelling is done on the log scale, all reconciliation is carried out on the original scale.  The fact that the constraints do not hold on the log scale is therefore not relevant.\\

		On re-reading the paper we do agree with the referee that there is scope for confusion here.  Therefore we have added some additional exposition to the beginning of section 4.1.  The aim here is to make it clear that after producing forecasting on some tranformed scale, the correct sequence of steps is to 1) back-transform to the original scale, 2) bias correct and 3) reconcile. \\

		\textit{When the empirical evaluation is focused on bias, then it would make sense to include an error that measures bias in addition to the squared error.}\\

		We now also report the total error for all methods to highlight bias.  Here we see that bias correction method 1 removes bias, while bias correction method 2 in fact worsens bias.  A new insight that we are able to make is to recognise that reconciliation without bias correction can mitigate bias.  For example, even if bias correction is not used at all, OLS reconciliation significantly reduces bias for both the log transformation and Box Cox transformation.  This is likely to occur since bias lies in a direction that is almost orthogonal to the coherent subspace.\\

@@

		\textit{Moreover, simply showing the MSE without any confidence intervals or measures of significance is not sufficient for the reader to assess the results.  It would also be useful to show the MSE relative to the base forecasts or the percentage improvement that is obtained.} \\

		We now include report all results relative to the base forecasts. We also have added starts to the tables that report our results to indicate when a method significantly upon base forecasts.\\

### 2020-01-22 R1/Letter.tex
changes made to response documents

Please find attached a revised manuscript for ``Forecast reconciliation: a geometric view with new insights on bias correction" by Anastasios Panagiotelis, Puwasala Gamakumara, George Athanasopoulos and Rob Hyndman for your consideration for publication in International Journal of Forecasting. We are very excited to have been given the opportunity to revise and resubmit. We carefully considered the comments offered by the two reviewers. Herein, we briefly summarize the major changes in the revision:
\begin{enumerate}
	\item blah
\end{enumerate}

>>>>

Please find attached a revised manuscript for ``Forecast reconciliation: a geometric view with new insights on bias correction" by Anastasios Panagiotelis, Puwasala Gamakumara, George Athanasopoulos and Rob Hyndman for your consideration for publication in International Journal of Forecasting. We are very excited to have been given the opportunity to revise and resubmit. We carefully considered the comments offered by the two reviewers. Herein, we briefly summarize the major changes in the revision:
\begin{enumerate}
	\item We introduce a modification of MinT that should be implemented in contexts where some user defined loss function is sensible.  Using the empirical example, we demonstrate that this generalised version of MinT takes both the nature of the loss function and dependence between forecast errors into account and outperforms a standard implementation of MinT and WLS.
	\item We have greatly expanded the empirical study including more measures of forecast accuracy (including those specifically measuring bias).  This has led to the insight that reconciliation alone can in fact reduce the bias of an estimator.  Where differences in forecast accuracy are significant.
	\item We now reflect on some issues that were not discussed in the previous version of the manuscript including the role of non-negativity, 
\end{enumerate}
